MAESTROeX: A Massively Parallel Low Mach Number Astrophysical Solver

### 2019-07-11 MAESTROeX_I/results.tex
updated amr results and added comments

In the planar case, we use the same problem setup for a hot bubble rising in a white-dwarf environment as described in Section 6 of Paper V. Here we use a domain size of $3.6\times 10^7$ cm by $3.6\times 10^7$ cm by $2.88\times 10^8$ cm, and allow the grid structure to change with time. The single-level simulation at a resolution of $128^2 \times 1024$ was run on Cori Haswell with 48 processors and took approximately 33.5 s per time step (averaged over 10 time steps) using either the original or new temporal algorithm. The adaptive simulation has a resolution of $32^2 \times 256$ at the coarsest level, resulting in the same effective resolution at the finest level as the single-level simulation. We tag cells that satisfy $T-\bar{T} > 3\times 10^7$ K as well as all cells at that height. The adaptive run took only 3.7 s per time step, and this 89\% decrease in runtime is mostly due to the fact that initially only 6.25\% of the cells (1,048,576 out of $128^2 \times 1024$ cells) are refined at the finest level. Figure \ref{fig:bubble_results} shows a series of planar slices of the temperature profile at time intervals of 1.25 s, and verifies that the adaptive simulation is able to capture the same dynamics as the single-level simulation at much lower computational cost.

@@

We continue to use the full-star white dwarf problem described in Section \ref{sec:whitedwarf} to test adaptive simulations on spherical geometry. The adaptive grid is refined twice by tagging the density at $\rho > 5\times 10^7$ g cm$^{-3}$ on the first level and $\rho > 10^8$ g cm$^{-3}$ on the second level. The simulation on a single-level grid of $512^3$ resolution took 26.01 s per time step (again averaged over 10 time steps).  The adaptive grid has a resolution of $128^3$ at the coarsest level and an effective resolution of $512^3$ at the finest level. On this grid, 8.9\% of the cells (1,493,504 out of $256^3$ cells) are refined at the first level and 5.3\% (7,176,192 out of $512^3$ cells) at the second. The adaptive simulation took 11.55 s, resulting in more than a factor of 2 in speedup. Both simulations are computed to $t=400$ s and we choose to use the peak temperature as the diagnostic to compare the results. Figure \ref{fig:wdconvect_amr_Tmax} shows the evolution of the peak temperature for all three runs and shows that the adaptive simulation gives the same qualitative result as the single-level simulation. We do not expect the curves to match up exactly because the governing equations are highly nonlinear, and slight differences in the solution caused by solver tolerance and discretization error can change the details of the results. Each simulation was run on Cori KNL with 512 processors and 16 threads per core.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htb]
\begin{center}
\includegraphics[width=4.0in]{./figs/wdconvect_amr_Tmax}
\caption{\label{fig:wdconvect_amr_Tmax} Peak temperature, $T_{\text{peak}}$, in a white dwarf from $t=0$ to $400$ s
         for grids with effective resolution of $512^3$. We can see that the adaptive grids with two levels of
         refinement give very similar solution trends compared to the single-level grid.}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

In the planar case, we use the same problem setup for a hot bubble rising in a white-dwarf environment as described in Section 6 of Paper V. Here we use a domain size of $3.6\times 10^7$ cm by $3.6\times 10^7$ cm by $2.88\times 10^8$ cm, and allow the grid structure to change with time. The single-level simulation at a resolution of $128^2 \times 1024$ was run on Cori haswell with 48 processors and took approximately 33.5 s per time step (averaged over 10 time steps) using either the original or new temporal algorithm. The adaptive simulation has a resolution of $32^2 \times 256$ at the coarsest level, resulting in the same effective resolution at the finest level as the single-level simulation. We tag cells that satisfy $T-\bar{T} > 3\times 10^7$ K as well as all cells at that height. The adaptive run took only 3.7 s per time step, and this 89\% decrease in runtime is mostly due to the fact that initially only 6.25\% of the cells (1,048,576 out of $128^2 \times 1024$ cells) are refined at the finest level. Figure \ref{fig:bubble_results} shows a series of planar slices of the temperature profile at time intervals of 1.25 s, and verifies that the adaptive simulation is able to capture the same dynamics as the single-level simulation at much lower computational cost.

@@

We continue to use the full-star white dwarf problem described in Section \ref{sec:whitedwarf} to test adaptive simulations on spherical geometry. The adaptive grid is refined twice by tagging the density at $\rho > 10^5$ g cm$^{-3}$ on the first level and $\rho > 10^8$ g cm$^{-3}$ on the second level. 
\MarginPar{possibly mention that we found the code encounters numerical difficulties when the tagging values are too close to each other in subsequent levels of refinement}
The simulation on a single-level grid of $512^3$ resolution took 12.7 s per time step (again averaged over 10 time steps).  The adaptive grid has a resolution of $128^3$ at the coarsest level and an effective resolution of $512^3$ at the finest level. On this grid, 27.8\% of the cells (4,666,880 out of $256^3$ cells) are refined at the first level and 5.3\% (7,176,192 out of $512^3$ cells) at the second. The adaptive simulation took 5.61 s, resulting in more than a factor of 2 in speedup. Both simulations are computed to $t=2000$ s and we choose to use the peak temperature as the diagnostic to compare the results. Figure \ref{fig:wdconvect_amr_Tmax} shows the evolution of the peak temperature for all three runs and shows that the adaptive simulation gives the same qualitative result as the single-level simulation. We do not expect the curves to match up exactly because the governing equations are highly nonlinear, and slight differences in the solution caused by solver tolerance and discretization error can change the details of the results. Each simulation was run on Cori haswell with 512 processors and 4 threads per core.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htb]
\begin{center}
\includegraphics[width=4.0in]{./figs/wdconvect_amr_Tmax}
\caption{\label{fig:wdconvect_amr_Tmax} Peak temperature, $T_{\text{peak}}$, in a white dwarf from $t=0$ to $2000$ s
         for grids with effective resolution of $512^3$. We can see that the adaptive grids with two levels of
         refinement give very similar solution trends compared to the single-level grid.}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
